---
title: "GoFordProj"
author: "Team"
date: "4/24/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(cache = TRUE, message = FALSE, warning = FALSE, root.dir = '/tmp')
```

## Loading necessary libraries.

```{r cars}
library(data.table)
library(ggplot2)
library(dplyr)
library(stringr)
library(rvest)
library(lubridate)
```

## Upload weather data from weatherunderground.com

```{r}
page1 = "https://www.wunderground.com/history/airport/KSFO/2017/6/28/CustomHistory.html?dayend=31&monthend=12&yearend=2017&req_city=&req_state=&req_statename=&reqdb.zip=&reqdb.magic=&reqdb.wmo="

p1 = page1 %>%
  read_html() %>%
  html_nodes(xpath = '//*[@id="obsTable"]') %>%
  html_table()

#Get the dataframe from the list
weatherhist = p1[[1]]
```

#In the weatherhist data frame, the headers repeat each month, so we will need to clean that up. 
#Will also need to change how the date appears in the first column and rename to something besides "2017". 
#As the data is,it is just the number of the day with no association to which month. The month is only in the row header. 

```{r}

bikedata17 = fread("2017-fordgobike-tripdata.csv", stringsAsFactors = F)
bikedata181 = fread("201801_fordgobike_tripdata.csv", stringsAsFactors = F)
bikedata182 = fread("201802_fordgobike_tripdata.csv", stringsAsFactors = F)
bikedata183 = fread("201803_fordgobike_tripdata.csv", stringsAsFactors = F)
#fread() is part of the data.table package in R and they perform significantly faster than the base read.csv() and write.csv() functions.

bikedata <- rbindlist(lapply(c("2017-fordgobike-tripdata.csv","201801_fordgobike_tripdata.csv","201802_fordgobike_tripdata.csv","201803_fordgobike_tripdata.csv"),fread))
#code above combine all the csv files together

bikedata$start_time <- ymd_hms(bikedata$start_time)
bikedata$end_time <- ymd_hms(bikedata$end_time)

#Have the start and end times be read as dates. 


```


