---
title: "GoFordProj"
author: "Team"
date: "4/24/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(cache = TRUE, message = FALSE, warning = FALSE, root.dir = '/tmp')
```

## Loading necessary libraries.

```{r cars}
library(data.table)
library(ggplot2)
library(dplyr)
# String manipulation
library(stringr)
# Parsing of HTML/XML files  
library(rvest)
# Eases DateTime manipulation
library(lubridate)
```


#In the weatherhist data frame, the headers repeat each month, so we will need to clean that up. 
#Will also need to change how the date appears in the first column and rename to something besides "2017". 
#As the data is,it is just the number of the day with no association to which month. The month is only in the row header. 

```{r}

bikedata17 = fread("2017-fordgobike-tripdata.csv", stringsAsFactors = F)
bikedata181 = fread("201801_fordgobike_tripdata.csv", stringsAsFactors = F)
bikedata182 = fread("201802_fordgobike_tripdata.csv", stringsAsFactors = F)
bikedata183 = fread("201803_fordgobike_tripdata.csv", stringsAsFactors = F)
#fread() is part of the data.table package in R and they perform significantly faster than the base read.csv() and write.csv() functions.


#Combine all the csv files together
bikedata <- rbindlist(lapply(c("2017-fordgobike-tripdata.csv","201801_fordgobike_tripdata.csv","201802_fordgobike_tripdata.csv","201803_fordgobike_tripdata.csv"),fread,stringsAsFactors = F))



#Have the start and end times be read as dates. 
bikedata$start_time <- ymd_hms(bikedata$start_time)
bikedata$end_time <- ymd_hms(bikedata$end_time)


#See the date range
range(bikedata$start_time)
```

## Upload weather data from weatherunderground.com

```{r}
#Upload all the weather data from weatherunderground.com

page1 = "https://www.wunderground.com/history/airport/KSFO/2017/6/28/CustomHistory.html?dayend=31&monthend=3&yearend=2018&req_city=&req_state=&req_statename=&reqdb.zip=&reqdb.magic=&reqdb.wmo="

p1 = page1 %>%
  read_html() %>%
  html_nodes(xpath = '//*[@id="obsTable"]') %>%
  html_table()

#Get the dataframe from the list
weatherhist = p1[[1]]

# Too messy with extra rows of column names


# Try to rebuild the table by combining weather data in each month

# June only contain the last 3 days' data, so the url pattern is different
page176 = "https://www.wunderground.com/history/airport/KSFO/2017/6/28/CustomHistory.html?dayend=30&monthend=6&yearend=2017&req_city=&req_state=&req_statename=&reqdb.zip=&reqdb.magic=&reqdb.wmo="

# Other months could be collected via specific pattern url.
months_2017 = c(7,8,9,10,11,12)
months_2018 =c(1,2,3)

# Urls
url.base2017 <- "https://www.wunderground.com/history/airport/KSFO/2017/"
url.base2018 <- "https://www.wunderground.com/history/airport/KSFO/2018/"
url.end <- "/1/MonthlyHistory.html?req_city=&req_state=&req_statename=&reqdb.zip=&reqdb.magic=&reqdb.wmo="
urls2017 <- paste0(url.base2017,months_2017,url.end)
urls2018 <- paste0(url.base2018,months_2018,url.end)

# Lists of weather data
p17list <- lapply(c(page176,urls2017), function(i) {
    read_html(i) %>%
    html_nodes(xpath = '//*[@id="obsTable"]') %>%
    html_table()
})

p18list <- lapply(urls2018, function(i) {
    read_html(i) %>%
    html_nodes(xpath = '//*[@id="obsTable"]') %>%
    html_table()
})

# Change the column name and add Date
#2017
for ( i in 1:length(p17list)) {
  month <- p17list[[i]][[1]]
  names <- month[1,]
  names[,length(names)]<-""
  month <- month[-1,]
  coln <- colnames(month)
  colnames(month)<- paste(coln,"-",names)
  month$Date <- ymd(paste(colnames(month)[1],month[,1]))
  p17list[[i]][[1]]<- month[,-1]
}
#2018
for ( i in 1:length(p18list)) {
  month <- p18list[[i]][[1]]
  names <- month[1,]
  names[,length(names)]<-""
  month <- month[-1,]
  coln <- colnames(month)
  colnames(month)<- paste(coln,"-",names)
  month$Date <- ymd(paste(colnames(month)[1],month[,1]))
  p18list[[i]][[1]]<- month[,-1]
}
# Combine the new table
p17list2 <- do.call(rbind, p17list)
final17 <- do.call(rbind, p17list2)
p18list2 <- do.call(rbind, p18list)
final18 <- do.call(rbind, p18list2)

weatherhist <- rbind(final17,final18)
rownames(weatherhist) <- NULL

weatherhist = weatherhist %>% select(Date, colnames(weatherhist)[-1])
```
